\chapter{Conclusion}\label{ch:conclusion}
This report illustrates the ease of which a full-stack web application can be developed and deployed from the
ground up with the best industry standards using AWS\@.
Being able to create a highly available, fault-resistant service is crucial for businesses trying to serve SaaS
applications to their users, and this report demonstrates how this can be done by any developer today.
The security policies that can be enabled easily within AWS, as well as how easy it is to create a robust fault-tolerant
infrastructure from within AWS, makes it an ideal platform for all web developers to at least consider using.

The project was highly successful, as all the necessary services to deploy \textit{Digital-Ink} were deployed in an
efficient, secure, and highly-available manner.
Additionally, the deployments were configured optimally, and this can be seen from the reasonable cost estimates made
for all scales of deployment.
The testing conducted on the deployed web application also highlight the accuracy to which the individual AWS services
were utilised.

Unfortunately, there were limitations to this deployment.
Several of these have been detailed within Chapter~\ref{ch:future-enhancements} Future Enhancements.
Notably, several of these enhancements were intended to be implemented when the deployment process began, however, the
accounts granted had restricted access to several of the features which were intended to be used.

In a future deployment of \textit{Digital-Ink}, it would be important to continue to be aware of the costs accumulated
by utilising the different infrastructure services.
Fortunately, the time and services spent configuring this deployment did not use up a significant amount of costs, and
estimates for future deployments are positive.
