\chapter{Cost Breakdown}\label{ch:cost-breakdown}

If we wished to deploy this web app to the public, or to expand it to a larger market, it would be important to
gather estimated costs for hosting the app in the cloud with all the AWS services being used.
We can use the AWS Pricing Calculator to calculate current costs and predict future costs.
To calculate these costs, it is required to specify every implemented feature and several projected inputs and outputs,
such as amount of data transferred on the app per month.
We began by calculating a monthly cost and a yearly cost of deploying the app in its current state.
Following this, we used the calculator to predict monthly a

In order to predict costs for the use of the AWS infrastructure, estimates from the official AWS
calculator were utilized. The AWS calculator required every implemented feature to be
inserted, as well as the projected inputs/outputs. E.g. how much data is transferred in a month.
The predicted monthly costs and yearly costs were output by the calculator given the present
state of the application on AWS. Following the initial prediction obtained from the AWS
calculator, those figures were used to create other scenarios for if the application gained 1000
to 10000000 users. The figures are used to estimate the costs when the application is scaled
up.


\section{Estimated Costs}\label{sec:estimated-costs}


\section{Scaling Up to 10,000 Users}\label{sec:scaling-up-to-10000-users}


\section{Scaling Up to 1 Million Users}\label{sec:scaling-up-to-1-million-users}


\section{Scaling Up to 10 Million Users}\label{sec:scaling-up-to-10-million-users}
